Title

### 2020-08-04 paper.tex
Adds Nam dielectric function description
Tightens verb choice
Fixes whitespace.
Adds missing coherence factor
Adds noise and reflection coefficient expressions.

@@

\begin{itemize}
	\item Include Nam expressions from~\cite{Nam1967}, including the choice for particle density function etc.
	\item Are there any interesting plots for Nam dielectric function?
	We're not adding anything to them, so only interesting thing is showing effect of frequency / temperature to show that Nam did indeed describe something that looks like a superconductor.
	\item Potentially include Lindhard expressions for completeness? or does it suffice to mention them.
	\item Include noise expressions from~\cite{QubitRelax} and~\cite{Henkel1999}.
	\item Include the Ford and Weber expressions in~\cite{Ford1984}, for reflection coefficients/ surface impedances.
	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
\end{itemize}

>>>>

\newcommand{\vf}{v_{\mathrm{F}}}

@@

	The relaxation rate for an electric qubit with dipole moment $\vec{d}$ a distance $r$ from a half space, described in~\cite{Henkel1999} and~\cite{QubitRelax}, can be written
	\begin{equation}
		\frac{1}{T_1} = \frac{d^2}{\hbar \epsilon_0} \frac{\omega^3}{c^3} \chi_{i}^{E}(r, \omega) \coth\frac{\omega}{2 T}.
	\end{equation}
	For a qubit pointing perpendicular to the surface of the half space,
	\begin{align}
		\chi_\perp^E(z, \omega) &= \Re \int_0^{+\infty} \dd{u} \frac{u^3}{v} e^{2 i z v} r_p(u).
	\end{align}
	Here, $z$ is measured in units of the vacuum wavelength $\frac{c}{\omega}$, $v = \sqrt{1 - u^2}$ and we take the root $v = i \sqrt{u^2 - 1}$ for $u \geq 1$.

	The reflection coefficients are described by Ford and Weber~\cite{Ford1984}:
	\begin{align}
		r_p(u) &= \frac{\epsilon(u) v - \sqrt{\epsilon(u) - u^2}}{\epsilon(u) v + \sqrt{\epsilon(u) - u^2}} \\
		r_s(u) &= \frac{v - \sqrt{\epsilon(u) - u^2}}{v + \sqrt{\epsilon(u) - u^2}}.
	\end{align}

	Nam~\cite{Nam1967} describes the electrodynamics for a broad class of superconducting behaviour.
	Assuming no magnetic impurities and weak coupling, we have
	\begin{equation}
		\epsilon(q = u \frac{\omega}{c}, \omega) = 1 + \frac{3 \pi}{\omega^2} \frac{n e^2}{m} \left[\int_{\Delta - \omega}^{\Delta}\dd{\omega'} \tanh(\frac{\omega + \omega'}{2 T}) I_1 + \int_{\Delta}^{\infty} \dd{\omega'} \left( \tanh(\frac{\omega + \omega'}{2 T}) I_1  - \tanh(\frac{\omega'}{2 T})I_2 \right) \right],
	\end{equation}
	with
	\begin{align}
		I_1 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[-\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		I_2 &= F(q, \Re[\sqrt{(\omega + \omega')^2 - \Delta^2} - \sqrt{\omega'^2 - \Delta^2}]) (g + 1) \nonumber\\
		&\quad + F(q, \Re[\sqrt{(\omega +  \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}]) (g - 1) \\
		F(q, E) &= \frac{1}{q \vf} \left[2 S(E) + (1 - S(E)^2)\ln(\frac{S(E) + 1}{S(E) - 1})\right]  \\
		S(q, E) &= \frac{1}{q \vf} \left( E - i \left(\Im[\sqrt{(\omega + \omega')^2 - \Delta^2} + \sqrt{\omega'^2 - \Delta^2}] + \frac{2}{\tau} \right) \right) \\
		g &= \frac{\omega' \left(\omega + \omega'\right) + \Delta^2}{\sqrt{\omega'^2 - \Delta^2}\sqrt{(\omega + \omega')^2 - \Delta^2}}.
	\end{align}

\begin{itemize}

	\item Are there any interesting plots for Nam dielectric function?
	We're not adding anything to them, so only interesting thing is showing effect of frequency / temperature to show that Nam did indeed describe something that looks like a superconductor.
	\item Potentially include Lindhard expressions for completeness? or does it suffice to mention them.
	\item Include noise expressions from~\cite{QubitRelax} and~\cite{Henkel1999}.
	\item Include the Ford and Weber expressions in~\cite{Ford1984}, for reflection coefficients/ surface impedances.
	\item Include 3D plot of noise vs $\omega$ and $T$ with presence of the phase transition to superconducting state?
	\item Include sample plot of noise vs distance here to show overall shape of noise (e.g. show levelling off for $z \rightarrow 0$ and cubic dependence further away, as expected?).
\end{itemize}
